%after finding requirements more research is needed.
\input{Research/macro_research}
\input{Research/Smart_Home_research}

\section{Router}
main question: How will the modular router be made?

\section{Sub-questions}
\begin{itemize}
    \item How big should the router be?
    \item What is the price that can be charged for the completed router?
    \item Who would use this product?
    \item How can the esp32 be used for the router?\cite{esp32_monitoring}
    \item how to flash an ESP32 board\cite{FlashingESP32}
\end{itemize}

\subsection{Methodology}
To answer the main question the sub-questions need to be answered. To answer the sub-question it is important to explain the methods used. The methods are given below. The sources for the research will mainly be searched with the google scholar search engine and Elsevier. 

\subquestion{1}{How big should the router be?}{2}
This question could be answered the best for how big routers are\\\\
\subquestion{2}{What is the price that can be charged for the completed router?}{2}
This will be done by looking at similar products that aim to have the same use.\\\\
\subquestion{3}{Who would use this product?}{2}
This can be done by asking people via a quiz or by searching for marketing stuff\\\\
\subquestion{4}{How can the esp32 be used for the router?}{2}
This is researched by searching for what the esp32 had been used before\\\\
\subquestion{5}{How to flash the esp32 board?}{2}
Looking at how people flash the esp32 and what the options are.
\\\\


\subsection{Size of the router}
In order to solve the size of the router it needs to compare different routers and see what can fit in a fuse box. 

\subsection{Price router}
This will be researched by looking at other comparable routers

\subsection{Users}
What kind of people would use the product.

\subsection{The esp32}
It is a microcontroller

\subsection{Flashing the esp32}
To flash the esp32 there are two general options. Number one is that a devkit is used and places on top of the PCB or the esp32 will be placed directly in order to flash it from one PCB. This will be cheaper and make the PCB smaller.
