\newpage
%alle risico's onder elkaar
%\begin{landscape} 

%\vspace*{-4cm}
\thispagestyle{empty}
\section{risk analysis}
%\begin{center}
The risk analysis is shown in \autoref{tab:risico_analyse}. In this table the Risk is first discussed, after that the consequence will be given and lastly the solution will be given. After these three the impact and chance are given. The impact and chance are rated from 1 to 5 depending on the severity of the risk. 1 is barely an inconvenience while 5 means it can derail the whole project. The numbers are also color coded with.

\begin{enumerate}
\item green
\item lime
\item yellow
\item orange
\item red
\end{enumerate}

\newcounter{riskTableCounter}
\setcounter{riskTableCounter}{1}
%\hspace*{-1.8cm}
%\vspace*{-4.5cm}

\begin{longtable}{| c | p{3cm} | p{3cm} | p{4cm} | c | c | p{3cm} |}
    %%%% titles
    \hline
    \rowcolor{teal} & \textbf{Risk} & \textbf{Consequence} & \textbf{Solution} & \textbf{Impact} & \textbf{Chance} & \cellcolor{lightgray}\textbf{Notes} \\\hline
    \rowcolor{teal}& & & & \textbf{[1-5]} & \textbf{[1-5]} &\cellcolor{lightgray} \\\hline
    %%%% ITEM SETUP
    \rowcolor{cyan}\theriskTableCounter{} &
    \stepcounter{riskTableCounter}
    % contents
    Covid-19 comes back and the Netherlands will go in lockdown again.& Everybody can't go outside anymore which means the necessary equipment for testing is unavailable. & 
    Try to do as much as possible remotely &
    \cellcolor{yellow}3 &
    \cellcolor{green}1 &
    \cellcolor{lightgray}A lot of this project can be done remotely. The only problem would be the testing. Even if there is a lockdown there is a big chance the office is still open. 
    \\ \hline
    %%%% ITEM SETUP
    \rowcolor{teal}\theriskTableCounter{} &
    \stepcounter{riskTableCounter}
    % contents
    The PCB doesn't work, because of a hardware mistake&
    The hardware wont work which will cost time and money&
    It has to be tested again on a breadboard until it works and then the PCB will be changed accordingly. &
    \cellcolor{lime}2&
    \cellcolor{yellow}3&
    \cellcolor{lightgray}There is a chance this will happen and it will depend on the mistake what the impact will be, however there is a high chance it will not be a big issue.
    \\\hline
    %%%% ITEM SETUP
    \rowcolor{cyan}\theriskTableCounter{} &
    \stepcounter{riskTableCounter}
    % contents
    I get severely ill & 
    I wont be able to work because of the illness &
    Getting more time for the project or someone else will take over, this means clear documentation so it can be taken over easily &
    \cellcolor{red}5 &
    \cellcolor{green}1 &
    \cellcolor{lightgray}This will probably not happen and documentation will be ready if this is the case anyway.
    \\ \hline
    %%%% ITEM SETUP
    \rowcolor{teal}\theriskTableCounter{} &
    \stepcounter{riskTableCounter}
    % contents
    The laptop on which progress is made malfunctions or erases all files&
    All the work could be lost that was done offline. &
    Make sure the necessary files are stored on GitHub& 
    \cellcolor{yellow}3&
    \cellcolor{lime}2&
    \cellcolor{lightgray}Its not that big a problem because the documentation will be done online. Besides this everything will be updated on GitHub.
    \\ \hline
    %%%% ITEM SETUP
    \rowcolor{cyan}\theriskTableCounter{} &
    \stepcounter{riskTableCounter}
    % contents
    Running behind the schedule&
    The product will not be able to be done on time&
    Hold strictly to the planning and if it changes talk about it.&
    \cellcolor{yellow}3&
    \cellcolor{lime}2&
    \cellcolor{lightgray}
    \\ \hline
    %%%% ITEM SETUP
    \rowcolor{teal}\theriskTableCounter{} &
    \stepcounter{riskTableCounter}
    % contents
    Change in plans&
    The Job gets changed&
    If it is manageable try to keep the changes in mind, if not finish the original job&
    \cellcolor{orange}4&
    \cellcolor{green}1&
    \cellcolor{lightgray}This is very unlikely and it depends on the situation. 
    \\ \hline
    %%%% ITEM SETUP
    \rowcolor{cyan}\theriskTableCounter{} &
    \stepcounter{riskTableCounter}
    % contents
    Problems in shipping of hardware&
    The necessary components wont arrive&
    Try alternatives or simulate as much as possible if the alternatives aren't available either&
    \cellcolor{yellow}3&
    \cellcolor{yellow}3&
    \cellcolor{lightgray}
    \\ \hline
    %%%% ITEM SETUP
    \rowcolor{teal}\theriskTableCounter{} &
    \stepcounter{riskTableCounter}
    % contents
    Not enough communication with the client&
    Misunderstandings could happen or the progress of the project will not be correctly conveyed&
    Talk at least once per week with the client if possible&
    \cellcolor{yellow}3&
    \cellcolor{lime}1&\cellcolor{lightgray}
    \\ \hline
    \caption{Risk analysis}
    \label{tab:risico_analyse}
\end{longtable}


\newpage
